### 2016-09-13 paper/old_sections.tex
added a bit to numerical results, transplanted conclusion from thesis

>>>>

\begin{table}
\caption{Average times to solve inverse problem and obtain error estimate with mixed- and high-fidelity models and noisy datasets; all averages only over those datasets for which the high-fidelity problem converged when given the low-fidelity problem as an intial guess.}
%\label{tab:ref3D_newdata_times_diffmesh}
\centering
\begin{tabular}{ccc|c|c|c}
\cline{4-5} 
 & & & \multicolumn{2}{|c|}{Error Estimation} & \\
\cline{1-6}
\multicolumn{1}{|c|}{\multirow{3}{*}{Case}} & \multicolumn{1}{|c|}{\multirow{3}{*}{DOFs}} & Inverse & Auxiliary & Supplementary & \multicolumn{1}{|c|}{Total} \\
\multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & Problem & Variables & Adjoint & \multicolumn{1}{|c|}{Solution}\\
\multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & Time (s) &  Time (s) & Time (s) & \multicolumn{1}{|c|}{Time (s)}\\
\cline{1-6}
\multicolumn{1}{|c|}{LF}    & \multicolumn{1}{|c|}{9537}   & 16   & --  & -- & \multicolumn{1}{|c|}{--} \\ \hline
\multicolumn{1}{|c|}{MF01}  & \multicolumn{1}{|c|}{13147}  & 156  & 101 & 261 & \multicolumn{1}{|c|}{517} \\ \hline
\multicolumn{1}{|c|}{MF02}  & \multicolumn{1}{|c|}{17895}  & 304  & 175 & 183 & \multicolumn{1}{|c|}{662} \\ \hline
\multicolumn{1}{|c|}{MF03}  & \multicolumn{1}{|c|}{21001}  & 385  & 228 & 187 & \multicolumn{1}{|c|}{801} \\ \hline
\multicolumn{1}{|c|}{MF04}  & \multicolumn{1}{|c|}{24528}  & 347  & 202 & 193 & \multicolumn{1}{|c|}{743} \\ \hline
\multicolumn{1}{|c|}{MF05}  & \multicolumn{1}{|c|}{27984}  & 470  & 275 & 212 & \multicolumn{1}{|c|}{957} \\ \hline
\multicolumn{1}{|c|}{HF}    & \multicolumn{1}{|c|}{70785}  & 1185 & --  & --  & \multicolumn{1}{|c|}{1185} \\ \hline
\end{tabular}
\end{table}
%
